---
title: "Project 1: Predicting Boston Housing Prices"
author: "Lucas Murtinho"
date: "March 11, 2016"
output: 
  html_document:
    toc: yes
---

Since we must deliver a PDF along with the iPython notebook, I decided to do the PDF in R; I hope that's ok.

# Getting started

```{r getting_started}
library(MASS)
CLIENT_FEATURES = c(11.95, 0.00, 18.100, 0, 0.6590, 5.6090, 90.00, 1.385, 24, 680.0, 20.20, 332.09, 12.13)
housing_prices = Boston[,14]
housing_features = Boston[,-14]

```

# Statistical Analysis and Data Exploration

```{r}
# Number of houses in the dataset
total_houses = dim(housing_features)[1]

# Number of features in the dataset
total_features = dim(housing_features)[2]

# Minimum housing value in the dataset
minimum_price = min(housing_prices)

# Maximum housing value in the dataset
maximum_price = max(housing_prices)

# Mean house value of the dataset
mean_price = mean(housing_prices)

# Median house value of the dataset
median_price = median(housing_prices)

# Standard deviation of housing values of the dataset
std_dev = sd(housing_prices)

```

Boston Housing dataset statistics (in $1000's):

Total number of houses: `r total_houses`

Total number of features: `r total_features`

Minimum house price: `r minimum_price`

Mean house price: `r sprintf("%.3f", mean_price)`

Median house price: `r median_price`

Standard deviation of house price: `r sprintf("%.3f", std_dev)`
